### 2021-11-08 manuscript.Rmd
final edits prior to submission, added manuscript PDF and OSF+GitHub links

author_note: |
  All simulation data, analysis code, and research materials have been made publicly available on the OSF and GitHub and can be accessed at [link] and [link].

@@

keywords          : "sequential analysis, hypothesis testing, efficiency, estimation, bias"
wordcount         : "11,387"

@@

Fast-forward 80 years, and we find ourselves in a decade of unparalleled methods reform in psychological science [@nelson2018]. At the receiving end of these proposed reforms we often find the statistical power of hypothesis tests [@bakker2012; @button2013]; that is, the long-run probability of observing a statistically significant result ($p < \alpha$) for a given number of subjects and a hypothesized effect size [@morey2016].

@@

All data, code, and research materials are available at [link]. The study was not preregistered. This manuscript was created using `r cite_r("r-refs.bib")`.

@@

Earlier, we introduced the reader to two trade-offs of potential importance to the sequential hypothesis tester: long-run error control vs. short-run evidence and efficiency in hypothesis testing vs. accuracy in parameter estimation, respectively. The short-run conception of evidence on which the (Sequential) Bayes Factor is based, has been accused of throwing out the error control baby with the bathwater [@mayo2016: p.2]. I show here -- in line with previous work -- that with appropriate design choices, the SBF procedure (implemented with a lower degree of flexibility than in previous investigations) can have comparable error rates to its frequentist alternatives. When using the Sequential Bayes Factor procedure, however, researchers are recommended to run simulations [e.g., using the R package `BFDA`, @R-BFDA] to choose an optimal design.

As discussed earlier, the SBF allows researchers to specify their uncertainty regarding the effect size by means of a prior distribution. Thus, for researchers who wish to incorporate prior beliefs (e.g., because they work in a subject area with high uncertainty about expected effect sizes), the SBF presents an appealing research strategy [@stefan2020]. On the other hand, if a researcher wants robust (i.e., guaranteed) error control, group-sequential designs present an appealing research strategy.

@@

*Note.* One-tailed, two-sample *t* tests using, for the frequentist procedures,  $\alpha$ = .05, 1 - $\beta$ = 0.8 for $\delta$ = 0.5. *N*s per group per look are `r n_fixed`, 25, and `r n_p` for the Fixed Sample, Independent Segments, and Pocock-like hypothesis tests. For the O'Brien Fleming test, *N* = `r n_of[1]` per group for the first look, and `r n_of[2]` per group for the last two looks. All sequential procedures were set to a maximum number of $k_{max}$ = 3 looks. For the Sequential Bayes Factor, data was collected in (at most three) batches of 22 subjects per group, and the procedure was terminated when the one-tailed Bayes Factor was greater than or equal to 3 in favor of the null or the alternative hypothesis. Figure includes the median effect size estimate (the solid line is the naive estimate; the dashed line is the bias-adjusted estimate). The true effect size $\delta$ = 0.5.

@@

## Figure A1 
## *Distribution of Obtained Effect Sizes Using Fixed versus Independent Segments Hypothesis Testing*
\noindent
```{r, fig.heigth = 20}
knitr::include_graphics("appendix/figures/figureA1.tiff", dpi = 1200)
```

@@

## Figure A3 
## *Bias-Variance in Obtained Effect Sizes Using Fixed versus Independent Segments Hypothesis Testing*
\noindent
```{r, fig.height = 6, fig.width=11}
knitr::include_graphics("appendix/figures/figureA3.tiff")
```

>>>>

author_note: |
  All simulation data, analysis code, and research materials have been made publicly available on the OSF and GitHub and can be accessed at osf.io/veczn/ and github.com/shilaan/sequential-testing.

@@

keywords          : "sequential analysis, hypothesis testing, efficiency, estimation, bias"
wordcount         : "11,368"

@@

Fast-forward 80 years, and we find ourselves in a decade of unparalleled methods reform in psychological science [@nelson2018]. At the receiving end of these proposed reforms we often find the statistical power of hypothesis tests [@bakker2012; @button2013]; that is, the long-run probability of observing a statistically significant result (*p* $< \alpha$) for a given number of subjects and a hypothesized effect size [@morey2016].

@@

All data, code, and research materials are available at osf.io/veczn and github.com/shilaan/sequential-testing. The study was not preregistered. This manuscript was created using `r cite_r("r-refs.bib")`.

@@

Earlier, we introduced the reader to two trade-offs of potential importance to the sequential hypothesis tester: long-run error control vs. short-run evidence and efficiency in hypothesis testing vs. accuracy in parameter estimation, respectively. The short-run conception of evidence on which the (Sequential) Bayes Factor is based, has been accused of throwing out the error control baby with the bathwater [@mayo2016: p.2]. I show here -- in line with previous work -- that with appropriate design choices, the SBF procedure (implemented with a lower degree of flexibility than in previous investigations) can have comparable error rates to its frequentist alternatives. When using the Sequential Bayes Factor procedure, however, researchers are recommended to run simulations [e.g., using the R package `BFDA`, @R-BFDA] to choose an optimal design. As discussed earlier, the SBF allows researchers to specify their uncertainty regarding the effect size by means of a prior distribution. Thus, for researchers who wish to incorporate prior beliefs (e.g., because they work in a subject area with high uncertainty about expected effect sizes), the SBF presents an appealing research strategy [@stefan2020]. On the other hand, if a researcher wants robust (i.e., guaranteed) error control, group-sequential designs present an appealing research strategy.

@@

*Note.* One-tailed, two-sample *t* tests using, for the frequentist procedures,  $\alpha$ = .05 and 1 - $\beta$ = 0.8 for $\delta$ = 0.5. *N*s per group per look are `r n_fixed`, 25, and `r n_p` for the Fixed Sample, Independent Segments, and Pocock-like hypothesis tests. For the O'Brien-Fleming test, *N* = `r n_of[1]` per group for the first look, and `r n_of[2]` per group for the last two looks. All sequential procedures were set to a maximum number of $k_{max}$ = 3 looks. For the Sequential Bayes Factor, data was collected in (at most three) batches of 22 subjects per group. Figure includes the median effect size estimate (the solid line is the naive estimate; the dashed line is the bias-adjusted estimate). The true effect size $\delta$ = 0.5.

@@

## Figure A1 
## *Distribution of Effect Sizes Using Fixed versus Independent Segments Hypothesis Testing*
\noindent
```{r, fig.heigth = 20}
knitr::include_graphics("appendix/figures/figureA1.tiff", dpi = 1200)
```

@@

## Figure A3 
## *Bias-Variance in Effect Sizes Using Fixed versus Independent Segments Hypothesis Testing*
\noindent
```{r, fig.height = 6, fig.width=11}
knitr::include_graphics("appendix/figures/figureA3.tiff")
```
